\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

\begin{document}

\title{IELTS Speaking Part 2\&3\\
{\footnotesize \textsuperscript{*}Note: 9-12 season query}}

\author{\IEEEauthorblockN{Liu Zhaohong}}

\maketitle

\begin{abstract}
speaking draft for IELTS test part 2 and 3, including only new questions
\end{abstract}

\section{People}
\subsection{Describe a person you know who is from a different culture}
Leo Messi;
    \begin{itemize}
        \item Who he/she is
        \item Where he/she is from
        \item How you knew him/her
        \item How you feel about this person
    \end{itemize}

For me that person should be Leo Messi. I think almost everybody knows him or ever heard about him.
He is a football player from Argentina, with the nationality of both Spain and Argentina.
I heard stories about him in my primary school, probably the year 2010.
At that time Messi was still young, but he was already famous in the football area;

Firstly I thought Messi was a selfish man who only dribbled the ball by himself and never passes it to his teammates,
and knew nothing about the teamwork. But now, actually since 2014, I have become a big fun of him.
2014 is the year when the Brazil world cup were held.
If you are familiar with that cup, you must remember that the final was between Germany and Argentina,
and unfortunately, Argentina lost that game with Mario Gotze scored at 114 minute.
It's really sad because Messi and his teammates had several good chances before that goal.
However, they didn't make it, I mean the chance didn't convert to a score.
Sadly that match was just a start, Argentina lost another American cup final in the last 2 years.
For Messi himself, Barcelona was turned over twice at the European Champions League.

I remember once during that time, Messi quitted the nation team because suffering from so many failures.
But finally he came back again and led Argentina team for the 2018 World cup, sadly lost again.

Looking at Messi's career, you will see with such talents and diligence of him, failure still could
be a common thing. I like his dribbling skills, which is really attractive, and I also like his humble personality.
But most of all, I like his behavior that a man can be defeated, but sooner or later he should stand up
then facing and overcoming those obstacles.
This give me the bravery to handle my daily failure, too.

\textit{1. How can we get to know people from different cultures better?}

first of all, respect; which means keep a humble profile and better know some of his or her culture.
Especially the taboo in that culture;

Second one is to express any idea directly; That is to be simple, meet anything confusing, be free to say that
I don't know then ask;

For more or detailed understanding, read books or watch news. Movies is also a good way.

\textit{2. What are the advantages and disadvantages of cultural diversity?}

Advantages include that, one can know different kinds of culture and that could be interesting;
different culture brings various custom, life style, these are the treasure of all human being.

Disadvantage might be, more possible conflict.
But that is not for certain. Different culture might take misunderstanding, and even account for fight and blood.
However, that can be avoided by peaceful communication.   

\textit{3. How can traditional culture and other cultures coexist?}

by finding similarity and ignore difference as much as possible.
focus on the similarity or the double-win staff.


\subsection{Describe a person who is fashionable}
My girlfriend;

\begin{itemize}
    \item Who he/she is
    \item What he/she does
    \item What kind of clothes he/she wears
    \item And explain why you think this person is fashionable
\end{itemize}

Okay I'm gonna talk about my girlfriend, the closest fashionable person to me.
currently she is a postgraduate student like me, and we were schoolmates during the undergraduate period.
There is a slang in China that a swift horse needs a high quality saddle to utilize its strength, so does a man, 
who needs suitable clothes.

I think a woman, or paticularly my girlfriend, has 2 accounts;
one account is used in campus, another one is for entertainment, and they are quite different.
In campus she usually wears simple and comfortable clother, like sports clothes.
I mean a pair of sneakers, a pair of loose pants, some daily T-shirt or hoodie.
However, that's another story for the recreation part;
That include dress, all kinds of coats, jackets, shoes and so on.
By the way, also including different colors of dyed hair;

While the most fashionable thing about her is not the clothes that she wear, but the combination of them.
I mean, maybe each clothes is a simple one, without complex design or various logos and icons, some of
them even seems plain and simple.
But my girlfriend got the magic to organize them (mixture and fusion and integration).
It's like she is solving a math problem that by which means of arranging the combination will bring highest fashion score.

So fashion is kind of knowledge and witness I guess.
Unfortunately I'm the one who know nothing about fashion, so I'm lucky to have her as my coach on dressing.

\textit{1. Are older people as fashionable as young people?}

I think there is no coorelation between age and fashion.
My opinion is they may have diferent definition about what fashion is.
For example, people born in 1950s used to wear the same green uniform as the military,
to express their respect to PLA and that's their fashion.
China keeps developing, after the reform and opening up we accecpted more western cultures;
Till now, we define our own fashion, maybe each one have their own fashion.

\textit{2. Are women more fashionable than men?}

It seems so but I think this is a problem that does't have that obvious link with gender.

We may all believe that women spend more time on make up, to preen themselves.
But actually some men do it either.
It's not about gender about only related to whether this persion is a fashionable one or not.

\textit{3. Why is fashion more important to some people?}

I think being fashion make them feel more confident, and being confident means one can express him or herself
more bravely.

For example, being fashion for some introvert people is kind of mental hint, telling them they are good and be
free to say anything or do something, I guess.


\subsection{Describe a person you know who loves to grow plants}
some source said plants=vegetables and fruits, some add flowers

My dad;

\begin{itemize}
    \item Who this person is
    \item What he/she grows
    \item Where he/she grows those vegetable/fruits
    \item And explain how you feel about this person
\end{itemize}

That person is my dad. He was born in 1970s, and grew up in a small village in northern China.
His parents, namely my grandmother and father were farmers.

So he did a lot of farming works when he was young, and he kept studying during that time, 
finally with the reform and opening up and his hard work, he entered a agricultural university, majoring in vest.
But he didn't end up to be a vest, he was distributed to an anti-virus department after graduation.
Now he is working in a normal government department, nothing related to planting at all.

However, during these years, he still keeps his planting skills.
We lived in the top floor of a flat in the past. And we had an outdoor balcony there, 
so my father used that place as a natural field for planting Chinese chives(vegetables) and grapes.
and I remember each summer when I was young, we can eat our own grapes, although so many of them were eaten by
passing-by birds and bees, so actually only a few left for us.
We once kept a dog, my dad found him near a dustbin homelessly so he took him back home and raised him.
and that dog destroyed many of his vegetables, dad didn't blame him, we just didn't have our own chives to make
dumplings those days.

Except for the balcony stuff, dad also have many flowers inside the room, each time they blossom dad will take
pictures and share that to his friends.

I think the purpose of planting has changed for him.
In the past when he was young, he had to do farm work to help his family.
When he grew older and got to work in the city, he had no need for that farm work,
till now, watering the flowers and other works look like a hobby, or an addiction for him.
I guess that's because there is farmer's blood in his vein.

\textit{1. What do you think of the job of being a farmer?}

I think it's quite normal, being a farmer is also a job in the whole social life.
And I believe that there shouldn't be discrimination against farmers, ranking them as the lowest of this society;
reason is simple cause no farmers, no food, no anything.

\textit{2. Are there many people growing their own vegetables now?}

Farmers still occupy a considerable part of population in China, and they surely grow their vegetables.
But for people living in cities, I don't think many of them have the time, skill and space to grow their own vegetables.


\subsection{Describe your favorite childhood friend}
My neighbor;

\begin{itemize}
    \item Who he/she is
    \item Where you met each other
    \item What you often did together
    \item And explain what made you like him/her
\end{itemize}
% who and where met
The childhood friend that I'm gonna talk about is my neighbor's son. He is also my neighbor either.
You know this neighbor I'm saying is not we lived in the same building but, in the same floor and door to door.
He is 4 years older than me, and I don't remember when we met.
Because I guess when we met is really a historical problem, maybe his mother took him to see my mother and me
just after I was born safely.

% often did together
We did a lot of things together, but there are some remarkable ones.
When I was 7 or 8, in my primary school period. Some buildings were dismantled near my home, because
they are too old and the city wanted to build some new stuff.
You know, the dismantle and construct departments are 2 different department.
So there is quite a time span that the ruin stayed there. And one night, we picked up some branches
, papers and a lighter to set up fire for barbecue.
and the food we baked is a corn.
I remember the lighting process is quite hard cause it's a little windy so we managed to light the paper first;
then using the burning paper to light branches, finally using steady fire to bake corn.
Actually that corn wasn't that delicious, but the process is interesting for me.

% digress a little
We also used to make paper plane then throw them at my outdoor balcony, to see whose plane could fly further.
and sometimes rode bicycle around the city in some nights. 

% what made like
To be honest, set up a fire on a mess of ruins is really dangerous. And except for that frenzy stuff,
he is also kind of my path-leader, after all he is older than me, so he did teach me some experience
that I used later.

\textit{1. Why do people lose contact with their friends after graduation?}

It has a lot of reasons;
First, we may spend more time with people around us. so without particular attention,
we might just forget to communication with old friends.

Secondly, if people go to work after graduation, the work load may cut greatly on their time
for social, causing the losing contact of old friends.

\textit{2. How does modern technology influence friendship?}

for truly friendship, technology makes 2 people get to know each other more quickly and precisely.
It's beneficial for keeping the friendship.

In the meantime, the time or cost to interrupt someone is also declined. If you make a call to your
friend directly while he is having an important conference with his volume on, that could be a miserable.

\textit{3. Do you think people's relationship with friends will change when they get older?}



\subsection{Describe a person who inspired you to do something interesting}
Leo Messi
\begin{itemize}
    \item \textbf{Who he/she is}\\
    For me that person should be Leo Messi. I think almost everybody knows him or ever heard about him.
    He is a football player from Argentina, with the nationality of both Spain and Argentina.

    I heard stories about him in my primary school, probably the year 2010.

    At that time Messi was still young, but he was already famous in the football area;
    \item \textbf{How you knew him/her}\\
    Firstly I thought Messi was a selfish man who only dribble the ball by himself and never passes it to his teammates,
    and know nothing about the teamwork. But now, actually since 2014, I have become a big fun of him.
    2014 is the year when the Brazil world cup were held.

    If you are familiar with that cup, you must remember that the final was between Germany and Argentina,
    and unfortunately, Argentina lost that game with Mario Gotze scored at 114 minute.
    It's really sad because Messi and his teammates had several good chances before that goal.

    However, they didn't make it, I mean the chance didn't convert to a score.
    \item \textbf{What interesting thing you did}\\
    Admiring his skill of dribbling and shooting, I started play football after the Brazil world cup.
    It's Messi led me the football area, get to know this sport.

    wasn't a technical player, the matches I involved ended up with loss and wins, so did some matches
    that you can see on the TV.
    \item \textbf{And explain how he/she inspired you to do something interesting}\\
    I think the most attractive and interesting part of football is its uncertainty and possibility.
    Like this time, Argentina lost to Saudi Arabic in the first group stage.

    Like years ago, in the last 5 minutes, Barcelona scored 3 goals and defeated Paris Saint German.
    That's the way he led me in and I found interesting.
\end{itemize}

\textit{1. What qualities make someone a role model?}

\begin{itemize}
    \item defeated but stand up again; 
    \item diligent; 
    \item chances to success; always fail is respectful, but the unknown let them lose the chance to be a model.
\end{itemize}

\textit{2. Who can influence children more, parents or teachers?}
\begin{itemize}
    \item teacher mainly on knowledge, but also some life experiences
    \item parents mostly on life experiences
    \item both important, can't figure out which one is more influential
\end{itemize}

\textit{3. Why should children learn from role models?}

\begin{itemize}
    \item like solving a math problem, first step is to learn the example, then extrapolating to other aspects;
    \item role models have some good quality;
    \item admire is a way to learn;
\end{itemize}


\section{Object}
\subsection{Describe a photo you took and you are proud of}

\begin{itemize}
    \item \textbf{When you took it}\\
    When I was a senior student in my undergraduate period, 2021's winter, 
    third year in my undergraduate life.

    \item \textbf{Where you took it}\\
    An old temple in Xi'an city, the foot of Qinling Mountains.

    \item \textbf{What is in the photo}\\
    My girlfriend stood under the roof of a corridor in that temple.

    And I was standing in the heavy snow, taking a picture of her.
    
    We were missing, nobody else was there, at that time she was looking for where should we go then.
    so she just lifted her head slightly and looked at far side;

    That is a traditional temple of Chinese Buddhism, there were pine trees behind the corridor, 
    they were all covered with snow;
    
    snow kept falling down, and the second when I took the shot, a piece of snow just passed by her eye. 
    Also you can see multiple pieces of snow in that picture. 
    
    \item \textbf{Explain why you are proud of it}\\
    in Chinese poems, we judge whether a scene is beautiful not only by the scenery, but also by the further emotion behind it;
    
    I think that picture express kind of emotion that although there is difficulty, namely the heavy snow and cold weather;
    and no one else was there to offer you a hand.
    then we have to think and look positively; although the weather is bad, it also gave us a beautiful picture.
\end{itemize}

\textit{1. Why do some people like to record important things by photos?}

\begin{itemize}
    \item  digital photos can be saved forever
    \item  convenient and easy to photo a schedule rather than writing down details
\end{itemize}

\textit{2. What can people learn from historical photographs?}

\begin{itemize}
    \item the truth of history, rape of Nanking
    \item clues to some unknown things
\end{itemize}

\textit{3. Is taking photo the best way to remember something?}

It depends.

\begin{itemize}
    \item knowledge, s simple photo might be useless
    \item cultural relic, function can't be replaced by photo
    \item a journey. photo is a good way.
\end{itemize}

\subsection{Describe an object that you think is beautiful}
describe a beautiful object
% 就写微博看到的火烧日照金山
\begin{itemize}
    \item \textbf{What it is?}\\
    It is a video about a peek of snow mountain.

    \item \textbf{Where you saw it?}\\
    I saw on the internet.

    \item \textbf{What it looks like?}\\
    Not sure about the time, morning or dusk.
    the  mountain is surrounded by rosy clouds, actually it's between golden and red.
    windy, so clouds keep moving.
    and it looks like the peek is set up fire and burning.

    \item \textbf{And explain why you think it is beautiful}\\
    contrast is attractive.

    it contains both static and motion, austere and feisty.

    the snow mountain is a static object, while clouds is in movement;
    the snow mountain consists of black and white, austere;
    while the clouds is red and golden, they are feisty.

    the contrast makes the video so beautiful.
\end{itemize}

\textit{1. Do you think there are more beautiful things now than in the past? Why?}

yes, cause we have more definition of beautiful things now.
\begin{itemize}
    \item in the past, they have relatively strict definition about what is beautiful
    \item and the existence of emperor, his will and preference could be so called beautiful
    \item currently, globalization makes one can get access to other culture
    \item the definition of beauty now is various
\end{itemize}

\textit{2. What beautiful scenic spot are there in your country?}
that will be plenty
\begin{itemize}
    \item northern China, pine forests and snow covered village
    \item southern China, sea, beach
    \item southwest China, rain forests, snow Mountains
\end{itemize}

\textit{3. Where do you think people usually come into contact with beautiful things?}
\begin{itemize}
    \item internet, Apps on smart phone
    \item friends, chat groups with similar interest
    \item TV, radio and so on
\end{itemize}

\textit{4. Why do you think people create beautiful things?}
\begin{itemize}
    \item work(painter, artist), aim is to create beauty
    \item hobby, occasionally create beauty, love doing with skill polishing, come up with
    \item total occasion, chancy
\end{itemize}

\subsection{Describe a movie you watched recently and would like to watch again}
% 万里归途吧就
\begin{itemize}
    \item \textbf{What it was about}\\
    It's a story about some diplomatic officers, evacuating oversea Chinese and took them back home.
    \item \textbf{Where you watched it}\\
    Two months ago, during the nation holiday, at my girlfriend's city.
    \item \textbf{Why you like it}\\
    Firstly, the main actor Zhang is a good role model in my opinion; (work hard, diligent, the eating noddle scene)
    
    Secondly, the scene is real, I can feel the chaos and danger caused by war at that country.

    Finally, the story itself is based on a true story. Reflect on the difficulty our diplomatic officers had met and
    their skills and faith to bring Chinese citizens back home.
    \item \textbf{And explain why you would like to watch it again}\\
    First, this movie is really attractive and moving.

    Second, I'm near sighted and didn't take my glass with me. 1080p ended up with 480p.
\end{itemize}

\textit{1. What are the differences between movies at home and in the cinema?}
\begin{itemize}
    \item atmosphere;people laugh, cry, sigh, scream
    \item dark, more concentrated and emotional
    \item new movie only accessible for cinema
    \item home is more convenient, talk, eat, everything you want
\end{itemize}

\textit{2. Do you think actors(or actresses) are important to the success of a movie?}
\begin{itemize}
    \item scripts, plot, story. fundamental of a movie
    \item actors' display is decisive
    \item a good actor or actress can't save plots or bad design(thoughtful)
\end{itemize}

\textit{3. Why are there fewer people going to the cinema to watch movies?}
\begin{itemize}
    \item covid-19, dangerous
    \item life and work is busy
    \item high expenditure
\end{itemize}

\subsection{Describe a program you like to watch}
\begin{itemize}
    \item \textbf{What it is?}\\
    I recently finished a really fascinating tv series called seal team.
    \item \textbf{What it is about?}\\
    And it's about a seal team six, DEVGRU bravo team, about each team guy's operation, life, even death.
    \item \textbf{Who you watch it with?}\\
    Actually I watched it myself cause on one has the same interest like me.
    \item \textbf{And explain why you like to watch it?}\\
    As a military program, the most important thing about seal team is its plot.
    The show doesn't pay all attention to illustrate the fighting scene, instead, it spend half of time on
    model main roles, from their families and minds.
    For example I think the most successful role is bravo six Clay Spenser.
    He grew from a green team guy to a tier 1 operator with his own duty, but sadly he was shot accidentally
    by a police, I really love and hate the life of him.
\end{itemize}

\textit{1. What programs do people like to watch in your country?}
\begin{itemize}
    \item TV series; 7 pm, after dinner whole family on the television
    \item clips; short and funny mostly, on bus, subway or anywhere; tiktok
\end{itemize}

\textit{2. Do people in your country like to watch foreign TV programs?}
\begin{itemize}
    \item some young people might prefer foreign TV programs
    \item Like Netflix, HBO, some Japan and South Korea programs
\end{itemize}

\textit{3. Do students watch programs in class in China?}
\begin{itemize}
    \item seldomly or never
    \item the study programs can be taught by teachers, so unnecessary
    \item something about culture and history might be used
    \item or news
    \item never for those recreation shows
\end{itemize}


\subsection{Describe an important thing you learned(not at school or university)}
not given up, Messi example
\begin{itemize}
    \item \textbf{What it is?}\\
    the valuable thing I gained is from football match, and that's trust on hope and never give up
    \item \textbf{When you learned it?}\\
    I got to know this probably from a particular match, that was Barcelona against Paris Saint German.
    \item \textbf{How you learned it?}\\
    Barcelona tried their best at that match, but when the match only had 5 minutes left, they still had 3 goals behind.
    Can you imagine 3 goals in the last 5 minutes? 
    I would never believe this could happen until I saw it myself. 3 goals in 5 minutes and turned over the game.
    After that I always believes that anything could happen if you stick to it and also with some luck. 
    \item \textbf{And explain why is was important}\\
    Always be hopeful is a valuable thing because, for example, it gives you faith to trust that underdogs could come through
    in a football match, you won't just turn off the TV and go to bed.

    More meaningfully, it is also a good quality to never give up in any obstacles met in daily life.
\end{itemize}

\textit{1. What can children learn from parents? What about grandparents?}
\begin{itemize}
    \item life experience, accumulated in their lives
    \item how to treat people, deal with people
    \item grandparents might mollycoddle children
\end{itemize}

\textit{2. Do you think some children are well-behaved because they are influenced by their parents?}
\begin{itemize}
    \item parents can have some influence on children 
    \item mainly depend on themselves
    \item instruct, information, tell how to do, but whether do or not is a self decision
\end{itemize}

\textit{3. Is it necessary for adults to learn new things?}
\begin{itemize}
    \item necessary for each person
    \item knowledge is updating fast, no learn, be left behind
\end{itemize}

\subsection{Describe a story or a novel that you have read and you found interesting}
I really like the chapter A Study in Scarlet in Sherlock Holmes
\begin{itemize}
    \item \textbf{When you read it?}\\
    It was several years ago, maybe in my junior high school time.
    At that Time I was crazy about detective novels.
    \item \textbf{What the story or novel was about?}\\
    The story is about a man revenge for his wife, not exactly is wife I remember.(loved one)
    He got a kill list, each person on that list is responsible for his wife's death.
    And each time he erased a name from that list, he will leave a message by blood, saying revenge.
    But it's german I remember, and at last Sherlock got him, but sadly the criminal died a few days
    after he was captured, because these years he had got severe illness.
    \item \textbf{Who wrote it?}\\
    By Arthur Conan Doyle
    \item \textbf{And explain why you found it interesting}\\
    It is so attractive because it's quite ambivalent.
    The criminal, actually is a brave and good man I think, he had no choices and he just want
    those who hurt his loved one to pay.
    They escaped, and from the law, and after I knew how he struggled to kill those bustards, but sadly died after
    his revenge. I don't know my feeling exactly, it's so complex at that time.
\end{itemize}

\textit{1. How does technology help people tell stories?}
\begin{itemize}
    \item e-book, read out the story while you lying on the bed
\end{itemize}

\textit{2. Why are mystery novels so popular these days?}
\begin{itemize}
    \item because people are always looking for something unknown
    \item and mystery novels satisfy people's need of solving problems
    \item maybe peep secrets, eager to get answer
\end{itemize}

\textit{3. What kinds of stories do children like?}
\begin{itemize}
    \item past, fairy tale
    \item now, all kinds, cultural integration and globalization
\end{itemize}


\section{Place}
\subsection{Describe a popular place for doing sports(e.g.stadium)}
playground.
\begin{itemize}
    \item \textbf{Where it is?}\\
    There are some small football pitches that are quite suitable for sports not only include football.
    They are in my university.
    \item \textbf{When you went there?}\\
    usually in the night, after 7 o'clock, it quiet;
    daytime is because I have gym class;
    \item \textbf{What you did there?}\\
    have football class, for 3 semesters;
    joining football match at night;
    with my girlfriend after class each night we would take a walk across the whole campus, then sit for a while at the playground.
    have dinner there(buy snacks, sit, eat); sometimes there are people singing.
    \item \textbf{And explain how you feel about this place}\\
    place was wonderful and memorable;
    remind me of my undergraduate life.   
\end{itemize}

\textit{1. What are the benefits of children doing sports?}
\begin{itemize}
    \item benefit health, physical strength
    \item teamwork and communication skills
\end{itemize}

\textit{2. Do young people like to do sports?}
\begin{itemize}
    \item It all depends
    \item some have physical requirement on themselves, so they do sports usually
    \item some are too busy to exercise, mostly
\end{itemize}

\textit{3. Is it necessary to build sports venues?}
\begin{itemize}
    \item yes, infrastructures are essential for some certain sports
    \item China football bad performance link up with few football courts in each city
\end{itemize}

\subsection{Describe the home of someone you know well and you often visit}
\begin{itemize}
    \item \textbf{Whose home it is?}\\
    the home I often go but not my home, that can only be my grandparents' home.
    \item \textbf{How often do you go there?}\\
    I go there when I'm in vacation, maybe once a week.
    \item \textbf{What it is like?}\\
    It's not so far from my home, it's in the same city so maybe 30 minutes' drive.

    in a big village, kind of row houses, with only one floor and four buildings.
    like a square(shape)

    a quite big garden is surrounded by the four buildings. grapes, flowers and some vegetables are planted in the garden.

    a big pot, meal cooked enough for 5 people, use wood as fuel.

    raise a dog as housekeeper.
    \item \textbf{And explain how you feel about the home}\\
    a traditional Chinese village house;
    quite from houses in cities.

    relaxed.
\end{itemize}

\textit{1. What are the differences between houses or buildings in the city and in the countryside?}
\begin{itemize}
    \item cities: small, crowded, shelter from sunlight, convenient
    \item village: quite, far from bustle and hustle, relax, inconvenient
\end{itemize}

\textit{2. Do you prefer to live in the city or in the countryside?}
\begin{itemize}
    \item young-city: better job opportunities, more convenient, all kinds of facilities, noisy and busy
    \item old-village: quiet, relax, fishing or do some farm work
\end{itemize}

\textit{3. What are the safety risks in residential buildings in cities?}

most are safe
\begin{itemize}
    \item fire, gas seep
    \item electricity accident
\end{itemize}

\textit{4. Is it expensive to decorate a house or an apartment in the place where you live?}
\begin{itemize}
    \item won't happen to me
\end{itemize}

\subsection{Describe a place in your country that you would like to recommend to
travelers}
Xian old city
\begin{itemize}
    \item \textbf{Where is it?}\\
    It's in the center of Xian city, Northwest China.
    \item \textbf{What is it?}\\
    It's Xian old city, surrounded by city walls built in 500 years ago.
    \item \textbf{What people can do there?}\\
    climb to the top of city walls through stairs;

    some famous snack street; Xian feature food;

    different kinds of bars at night, drink cocktail of eastern and western integration flavor;
    
    ride bicycle on the top of city walls;
    \item \textbf{And explain why you would like to recommend it to travelers}\\
    Xian itself is a historical city, with 3 thousand years history.
    Many cultural relics.

    The food there can be found at somewhere else in China, but totally different; Once tasted, know which better.

    The best place to know about China, even better than Beijing.
\end{itemize}

\textit{1. Is it important to take photos while traveling?}
\begin{itemize}
    \item Yes, to have some visual memory after the journey.
    \item share with others and recommend that place to them
\end{itemize}

\textit{2. Can we trust other people's travel journals on the internet?}
\begin{itemize}
    \item like state estimation, pose and position
    \item so many wrong and bad data points
    \item to some extend, use more data
    \item so it means to check more journals and gathering information from all of them 
\end{itemize}

\textit{3. What factors affect how people feel about their journey?}
\begin{itemize}
    \item transport; clean, fast, comfortable or not;
    \item weather; terrible for a rainy day if you want to see sunrise on a mountain top;
\end{itemize}

\section{Event}
\subsection{Describe a problem you had while shopping online or in a store}
\begin{itemize}
    \item \textbf{When it happened?}\\
    I met such problem several weeks ago.
    \item \textbf{What you bought?}\\
    when I bought a pair of pants.
    \item \textbf{What problems you had while shopping online?}\\
    However, it turned that what I got was totally different from the picture of this pants.

    The picture online showed that the pants was about light blue color, like the morning sky, crystal and clear.

    But I received a dark blue one, I really didn't like dark blue.
    And they had lots of options, I've seen the dark blue one there.
    So I believed that it's their mistake to send me a wrong color one.

    So I ask them to change one for me.
    However, they called this, color difference with picture and real thing.

    I can accept color difference, but that was totally different color.

    No option, so asked the shopping platform for help, they finally agreed to change one for me.
    \item \textbf{And explain how you felt about it}\\
    quite frustrated about the shop, pleased with the platform.
\end{itemize}

\textit{1. What kind of service do you think is good?}
\begin{itemize}
    \item communicate patiently, be respectful
    \item no private call for another time if the customer has expressed unwillingness 
\end{itemize}

\textit{2. What would you do if you bought something disappointing from the internet?}
\begin{itemize}
    \item I will talk to the shop that I'm sorry but that's what I want, then send it back and get my money back
    \item score system to express my disaffection
\end{itemize}

\textit{3. Do you think online shopping will replace in-store shopping in the future?}
\begin{itemize}
    \item no, in-store shopping has its advantages
    \item try it on to see if fit well
    \item go to the mall together for some people is a social activity, eat, buy some drinks then go shopping
\end{itemize}

\subsection{Describe a time when you made a decision to wait for something}
wait for applying ETH zurich.
\begin{itemize}
    \item \textbf{When it happened?}\\
    Several weeks ago, I made that decision to wait for applying ETH zurich. 
    \item \textbf{What you waited for?}\\
    It's a master program called master of robotics, system and control that I'm waiting for.
    \item \textbf{Why you made the decision?}\\
    Actually I'm already chasing for a master's degree at SJTU.

    However, the course and timetable was compulsory, and unfortunately I had no interest on most of courses they arranged for me;
    without asking my opinion;

    And we can't choose our internship, it's also fixed by leaders.

    The most disgraceful thing is that when they told me that I was enrolled in majoring in information and control,
    but I found what I'm learning has no relationship with control.

    And the next year is also full of class, no much time for own research.
    \item \textbf{And explain how you felt about the decision}\\
    I felt the decision was rather bold, taking a lot of risks;

    But ETH is my dream university and I really want to be a member of Autonomous Lab there.

    Won't regret.
\end{itemize}

\textit{1. Why do some people prefer slow-paced life?}
\begin{itemize}
    \item life cost is higher, people have to work harder, so they want to slow down to rest.
    \item slow-paced life has more time for oneself, whether doing what he like or accompany with his family.
\end{itemize}

\textit{2. Is it necessary for people to learn to be patient?}
\begin{itemize}
    \item patient is a good quality, it has a lot of benefits; work in order;
    \item but being bold sometimes can lead to unexpected results, even better than being patient;
    \item so it mainly depends on one's personality.
\end{itemize}

\textit{3. Are people less patient now than in the past?}
\begin{itemize}
    \item might be, life pace is becoming faster than past, so people tend to be less patient.
    \item society think more of personality, so being less patient might be useful in some occasions.
\end{itemize}

\subsection{Describe a time when you received money as a gift}
\begin{itemize}
    \item \textbf{When it happened?}\\
    The last time I got money from others except my parents was several days ago.
    \item \textbf{Who gave you the money?}\\
    But it's not from any person but from my damn school, my university.
    \item \textbf{Why he/she gave you the money?}\\
    Actually I believe my university doesn't spare a penny to me.

    But the money is from my country's education department, to give each postgraduate student 600 RMB each month as
    my subsidy to compensate my living cost.
    \item \textbf{And explain how you felt about it}\\
    I'm really thankful to my country but no so pleased with my university.

    Can you believe a QS ranking 50 university doesn't give master student a buck each month?
    Although we are not experienced researchers, we are also making contribution to this university and the society.

    so quite sad and disaffected about this.
\end{itemize}

\textit{1. Why do people rarely use cash now?}
\begin{itemize}
    \item inconvenient to take with
    \item mobile payment is safer and more convenient
    \item easy to broke or torn up
\end{itemize}

\textit{2. Do you think it is useful to give money as gifts?}
\begin{itemize}
    \item useful for red pockets
    \item useful for corruption
    \item useless as a gift
\end{itemize}

\textit{3. When do children start to realize the value of money?}
\begin{itemize}
    \item when they know how difficult it is to earn a penny
    \item young, use money from parents, know nothing
    \item older, chance to earn money themselves, know value
\end{itemize}

\subsection{Describe a disagreement you had with someone}
\begin{itemize}
    \item \textbf{Who you had the disagreement with?}\\
    Talking about disagreement, this often happens to me. And there is a time that I had disagreement with my girlfriend.
    \item \textbf{What the disagreement was?}\\
    Actually there was nothing about who is right and who is wrong.

    It's about the way we deal with disagreement that we disagree.
    \item \textbf{What happened?}\\
    In my opinion, when disagreement happened, we two both must be in bad mood, so we should speak carefully.
    and reasonably, to make the quarry clear, to see where is wrong.

    But she thought that emotion was more important than what the disagreement actually was.
    Which means, to comfort her first then fix the disagreement if necessary.

    But I might be so reasonable that every time I would dispute with her about what shouldn't do and where is wrong.
    \item \textbf{And explain how you felt about it}\\
    After each disagreement, I knew I was the one who made mistake, I should really take her feelings and emotion as the first thing.

\end{itemize}

\textit{1. What do you do if you disagree with someone?}
\begin{itemize}
    \item I will make my point clear again to see if there is anything misunderstand
    \item find something similar in different opinions
    \item no similarity and no misconstrue, no more to say
\end{itemize}

\textit{2. How do we stop an argument from escalating into a fight?}
\begin{itemize}
    \item first thing is to pull the two guys away, make them apart
    \item let each one of them to stop talking and calm down
    \item after that, talk 
\end{itemize}

\textit{3. What disagreements do parents and children usually have?}
\begin{itemize}
    \item study, homework, test score
    \item play games, watch TV or not
\end{itemize}

\subsection{Describe an outdoor activity you did in a new place recently}
% recent can be long time ago
\begin{itemize}
    \item \textbf{What the activity is?}\\
    It was a football match that happened a week ago.
    \item \textbf{Who invited you to participate in it?}\\
    My roommate called me in, although I hadn't been playing football for 3 years. 
    \item \textbf{Whether you ask for help during the activity?}\\
    So it was hard for me;
    I used to be a forward,more precisely a shadow striker on the pitch.
    However, if the striker is not so proficient, he might lose the control of the ball easily;
    which means, your opponent would have a good chance to lead an attack, that is dangerous.
    So I had to ask him for several times to watch my six and help me.
    \item \textbf{And explain what change had in the activity}\\
    And of course, with his help, I was more confident in the game.
    He also told me to be focus on avoiding the physical confrontation, because I'm too thin.
    After that our side had became more aggressive, although it's not my goal, we won the game eventually.
\end{itemize}

\textit{1. What outdoor activities are popular in China?}
\begin{itemize}
    \item basketball, almost every big park have several basketball courts
    \item ping-pong, that's China's national ball, even small park can have a table for it.
    \item cycling, getting more and more popular due to traffic jam, tend to love bike
\end{itemize}

\textit{2. What are the differences between after-class activities done by young and older children?}
\begin{itemize}
    \item sadly they may now all have to keep studying, but there can be a little difference
    \item younger kids, have more opportunities to develop their interested skills or hobbies
    \item while elder children, teenagers, have to study all kinds of classes to prepare for exams
\end{itemize}

\textit{3. Should young people try as many new activities as possible?}

It depends on their thoughts.
\begin{itemize}
    \item try different activities can help you find what you like;
    \item but focusing on several certain activities can hone your skill and give you satisfaction through success
\end{itemize}

\subsection{Describe a time when you forgot an appointment}
\begin{itemize}
    \item \textbf{What the appointment was for?}\\
    There was a time that I missed a meeting with my teacher and schoolmates. 
    We were gonna talk about the plan of how to carry out a program.
    \item \textbf{Who you made it with?}
    teacher and schoolmates, see above.
    \item \textbf{Why you forgot it?}\\
    I missed the meeting because I slept over and didn't get up on time.

    And that's because that night I was watching the Qatar World Cup, Argentina against Mexico.
    If lose, go home, so exciting.

    Last for 2 hours, before that I didn't sleep because I was to nervous.

    But finally, won; then I slept with relief and when I opened my eyes up, the meeting had started.
    \item \textbf{And explain how you felt about the experience}\\
    had started for an hour;

    nervous, afraid of messing up;

    also worthy for watching such a game.
\end{itemize}

\textit{1. How do people who are busy every day remember things they need to do?}
\begin{itemize}
    \item use a to do list, like Microsoft TODO
    \item set alarms
    \item make use of calendar on phone
    \item take notes
\end{itemize}

\textit{2. How do Chinese people know their family history?}
\begin{itemize}
    \item Chinese new year, sitting together chatting for a long time
\end{itemize}

\subsection{Describe a time when you shared something with others}
\begin{itemize}
    \item \textbf{What you shared?}\\
    There was a period that me and my roommate did a open-source program and shared it to our classmates.
    \item \textbf{Who you shared with?}
    classmates, see above.
    \item \textbf{Why you shared it?}\\
    Actually it's a course project of a quite challenging class.

    Most of our classmates have to prepare for the postgraduate enrolling exam.
    Time limited for them.

    We spent a long time to finish our work, we thought it can be used to help others.

    And an open-source project could be liked by other people, they can help to polish the program.
    \item \textbf{And explain how you felt about sharing it}\\
    The outcome was good, we did help lots of people.

    And the program received several comments about bugs and better algorithm.

    When I shared this program on the presentation, it even bought us pleasant from teachers.

    I felt it's really a beneficial thing, to make the program better and to help others.
\end{itemize}

\textit{1. What are the consequences if children don't know how to share?}
\begin{itemize}
    \item become selfish
    \item know nothing about teamwork
    \item low ability on communication
\end{itemize}

\textit{2. How do people feel about sharing accommodation with others on campus?}
\begin{itemize}
    \item depend on roommate, consensus in life regulation or not, like get up early or stay up late
    \item most people think it's would fine, college students can't afford buying a house or renting one either
\end{itemize}

\textit{3. How can parents and teachers teach young children to share?}
\begin{itemize}
    \item first is the power of teamwork
    \item use some role models
\end{itemize}

\subsection{Describe a time when you needed to search for some information}
\begin{itemize}
    \item \textbf{What information it was?}\\
    When I was doing my undergraduate project, I met a bug and I need to gathering information to solve it.
    \item \textbf{When you searched for it?}\\
    It's about one year ago.
    \item \textbf{How you searched for it?}\\
    I firstly just google the error message the application told me.

    But I found that the information I got was so cursory;
    So I entered some professional website like stackoverflow, and Pixhawk4 forum.

    Then I finally found a solution from a github issue. 
    \item \textbf{And explain why you needed to search the information}\\
    because I met a problem in experiment.

    I was using PX4, a flight control application. But no matter what command I gave to the drone, 
    it just didn't take off successfully.
    Something kept locking it up.

    Without taking off, I couldn't go on with further research.
\end{itemize}

\textit{1. How can people search for information now?}
\begin{itemize}
    \item website, internet, google
    \item use application on mobile phone
    \item ask others, like professional staff
\end{itemize}

\textit{2. With the development of the Internet, are libraries still important?}
\begin{itemize}
    \item although carrying a lot of books may be a big problem, but reading books are not that harmful to eyes as using computer screen.
    \item books can provide a better reading atmosphere
\end{itemize}

\textit{3. Does the development of the Internet have any influence on disadvantaged people?}
\begin{itemize}
    \item for example, blind people can't read e-books easily on a screen
    \item because books they read in touchable, use Braille
    \item but e-books, screen can't use Braille
\end{itemize}

\subsection{Describe a time when you saw a lot of plastic waste (e.g. in a park, on the beach
etc.)}
\begin{itemize}
    \item \textbf{Where you saw the plastic waste?}\\
    Last time I saw a lot of plastic rubbish was on a beach of Qinhuangdao city, north China.
    \item \textbf{When you saw the plastic waste?}\\
    It was dusk, when I and my girlfriend  went to a walk along the beach near our hotel.
    \item \textbf{What you did?}\\
    We founded that there was certain area of a beach that contained lots of plastic rubbish.

    We also saw an old man, bending to pick up those wastes and threw them in his big bag.
    And he was probably some volunteer guy, wearing an orange jacket.

    As we had nothing to do, so we joined him to clean up the beach together.
    I remember there were mainly plastic bottles, maybe tourists threw them away after drinking.

    About half an hour, we three finished this work.
    \item \textbf{And explain how you felt about this experience}\\
    A felt kind of achievement, like make contribution to the environment.

    But I still hope that we can be cautious about plastic bottles, do not throw them to the sea, that's
    harmful for sea animals.
\end{itemize}

\textit{1. Why do some people like to use plastic products?}
\begin{itemize}
    \item easy to carry
    \item inexpensive
    \item use many times
\end{itemize}

\textit{2. Do you think we should use plastic products?}
\begin{itemize}
    \item we can use for convenience
    \item but need to put them in the right dustbin
\end{itemize}

\textit{3. How can we reduce our use of plastic products?}
\begin{itemize}
    \item use something else instead, like glass bottle
    \item use green-plastic, can be resolved by soil
\end{itemize}

\textit{4. What kinds of plastic waste are often seen in your country?}
\begin{itemize}
    \item bottles
\end{itemize}

\subsection{Describe a time when you enjoyed an impressive English lesson}
\begin{itemize}
    \item \textbf{When and Where you had the lesson?}\\
    I remember there was an English class that left good impression on me.
    It 2 years ago at an English training center.
    \item \textbf{Who gave you the lesson?}\\
    The lesson was given by a Chinese female teacher. 
    \item \textbf{What the lesson was about?}\\
    About reading articles and papers in English.

    different, not like common reading, line to line.

    Guess reading, predict-reading. While reading, guess what would the author talk in the later chapter.
    next paragraph.
    \item \textbf{And explain why you enjoyed the lesson?}\\
    I enjoyed it because it's challenging.

    novel method for me to read articles. And I think the base of using this, is to have a clear mind about
    how to organize an article.
    Know the standard structure, also benefit for writing.

    learned a lot from it.
\end{itemize}

\textit{1. Is it interesting to be a foreign language teacher?}
\begin{itemize}
    \item I don't think so, to be a teacher means that you've already skilled at it.
    \item telling them the same thing that you already know for several times seems boring for me
    \item but someone like it
\end{itemize}

\textit{2. What makes a good foreign language teacher?}
\begin{itemize}
    \item be patient with students and has some teaching skill
    \item be mastered at his foreign language
\end{itemize}

\textit{3. Do you think language learning is important?}
\begin{itemize}
    \item for the globalization and communication, yes
    \item using their language not interpreter is more fluent in talk
\end{itemize}

\textit{4. Do you think grammar is important when learning foreign language?}
\begin{itemize}
    \item yes, but may not be so important at first
    \item a little skilled, attention on grammar, precise
\end{itemize}

\subsection{Describe a difficult thing you did and succeeded}
\begin{itemize}
    \item \textbf{What it was?}\\
    The hard thing I can remember was several months ago, a bug in my undergraduate project.
    \item \textbf{How you overcame the difficulties?}\\
    Search the error message on internet.

    Go to the software's website leave a message.

    Go to some professional forums, stackoverflow and PX4 forum.

    Ask a senior that I'm familiar with for help.
    \item \textbf{Whether you got help?}\\
    He was glad to help me.

    Sat there all day on a computer to test and trying to fix the bug.
    \item \textbf{And explain how you felt after you succeeded}\\
    Finally bug was fixed and we knew exactly what caused this bug and how to fix it.

    achievement after solving a problem. 
\end{itemize}

\textit{1. What kinds of things do children feel very hard to do?}
\begin{itemize}
    \item facing a problem that they never met before
    \item need too much knowledge to solve a problem
    \item need time if the child is less patient
\end{itemize}

\textit{2. How can parents encourage children to do something difficult?}
\begin{itemize}
    \item to instruct the way to solve a difficult problem
    \item teach them patiently, make them curious
\end{itemize}

\textit{3. What kinds of jobs can help people become confident?}
\begin{itemize}
    \item waiter or waitress, job need communication
    \item lawyer, must be confident to defend for clients 
\end{itemize}

\textit{4. What's your definition of success?}
\begin{itemize}
    \item reach the goal set before
    \item Positive outcome after hard effort and useful experience
    \item Achievement of goals that help others succeed
    \item A successful person is one who done his work properly.
\end{itemize}


\end{document}