\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

% 添加中文支持包
%\usepackage[UTF8]{ctex}
%\usepackage{CJKutf8}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}


\begin{document}

\title{Speaking Part 1\\
{\footnotesize \textsuperscript{*}Note:
9-12 season query}
}

\author{\IEEEauthorblockN{Liu Zhaohong}
}

\maketitle

\begin{abstract}
speaking draft for IELTS test
\end{abstract}

\begin{IEEEkeywords}
IELTS, Speaking
\end{IEEEkeywords}


\section{Study/Work}

\subsection{Do you work or are you a student?}
Student + Degree + School + Major(engineering)

I'm a post graduate student at SJTU currently.

Majoring in aircraft control and information engineering. 


\subsection{What subject are you studying?}
Aircraft control and information engineering.

mostly it's about control stuff, like control law's designing and modelling of an aircraft

\subsection{Why did you choose that subject?}
I liked it in my high School and I was interested in planes, aircraft, something stuff

So, I chose this subject as my bachelor's Major and kept learning it in my master's study



\subsection{What would you like to do in the future?}
to be a robotics engineer



\subsection{What are the most popular subjects in China?}
computer science

seems with higher salaries than other subjects you can remember

\subsection{Do you think it's important to choose a subject you like?}
after the bachelor's time span, I'd say it depends on what life stage we are in

during bachelor time, one can choose subjects that are more universal.

For engineering students, they are math, physics, electronics and computer science etc.
the base for further study.

While in post graduate period, interest is rather important because
one need the interest to support his determination on doing research

\subsection{Are you looking forward to working?}
depends on the ??? of master degree

suitable for doing research or better for industry

\subsection{Do you like your subject? Why or Why not?}
no; compulsory subjects are not reasonable for us 

control vs. material mechanics

\subsection{Do you prefer to study in the mornings or in the afternoons?}
mornings

eat a lot at lunch, and digesting need more oxygen so I always feel sleepy

\subsection{Is your subject interest to you?}
mostly not, but there is a subject named Optimization Method that I found really interesting to me

\subsection{Is there any kind of technology you can use in study?}
if programming and math are kinds of technology

\section{Hometown}

\subsection{Has your hometown changed much these years?}
hugely; a better word;

the word change applies for most cities of China, after the reform and open up

\subsection{Is that a big city or a small place?}
it's a middle city;
can't compare to capital city?(mind grammar);

middle but with high happiness(mind grammar)

\subsection{How long have you been living here?}
I guess it's referring to my hometown;

18 years, before I enrolled in collage;

\subsection{For you, what benefits are there living in a big city?}
several advantages;

first, there are some kinds of jobs that do not exist in small city, which means more opportunities;

second, better infrastructure

and, universities

\subsection{Is there anything you dislike about it?}
higher living cost

and???

\subsection{Where in your country do you live?}
Shanghai, cause I'm studying here

but my hometown is in northern China

\section{Accommodation}

\subsection{Are the transport facilities in your city very good?}
not So

last bus is at about 7 pm, a little inconvenient;
environment on the bus is good

\subsection{Which room does your family spend most of the time in?}
sadly I guess it's the dining room, when we eat meals

used to stay at the living room, for news and weather forecast

due to smartphones, more likely to lie on each bedrooms

\subsection{Do you live in a house or a flat?}
flat, actually dorm(related to student question, where live and what status
I'm in)

\subsection{Do you plan to live here for a long time?}
of course not, house price is an astronomical number for meals

it's a considerable problem to choose a big city or small city,
and house price is definitely a shortcoming for big city

\subsection{Do you live alone or with your family?}
live alone(related to student question) in dorm
cause I'm still a student and it's not affordable for me to rent a room here

\subsection{How long have you lived there?}
there?here?

here: for only 3 months, just enrolled inconvenient

there: ?

\subsection{What do you usually do in your home/house/flat?}
\begin{itemize}
    \item home; I'm still a enrolled in student so 
    there isn't much time for me to stay at home;
    \item flat; the workload is stressful for me;
    and while staying at dorm, I tend to relax instead of getting to
    those unfinished works; so I would go to sw else to study
\end{itemize}

\subsection{Which is your favorite room in your home?}
living room, with a big scale television and a spacious sofa

feel good lying there watching my favorite episodes

\subsection{What's the difference between 
where you are living now and where you lived in the past?}
If the question before is about ever moved house:

facilities are all renewed and with larger areas

If the question before is about place living now and home:

dorm is totally different from home, in almost every aspect;
like no television and sofa for me to relax

\subsection{What can you see when you look out the window of your room?}
    \begin{itemize}
        \item home: in China, If you are not the kind of rich guy, then
        it's probably that the building you are living in is next to another
        building. Then there goes 2 consequences, facing the street, located
        at the edge of the community or facing another building in your community
        \item flat(dorm): it's quite crowded in campus, the scenery I can see
        from my flat's window is another flat building
    \end{itemize}

\subsection{Would you be willing to live in the countryside in the future?}
If the future is I'm rich enough and kind of old, I will;

fighting for my whole life seems a unpractical goal for me,
and I want to relax when I'm old and got no worry about living

\section{Snacks}
Note: New Questions for Season 9-12

\subsection{What snacks did you eat when you were young?}
A famous Chinese traditional food named LaTiao;

TODO: how to describe

\subsection{Do you often eat snacks now?}
no, snacks seems not so healthy;

I'd rather spend that money on other things like saving money
for a trip

\subsection{Do you think eating snacks is healthy?}
It depends actually;
% 在这里我想说，有时候一丁点零食能够带来很大的幸福感，这时候就不用担心健康与否
for me, I can get 

\section{Birthday}
\subsection{What do you usually do on your birthday?}
interesting, my birthday is near the date of returning to school

so prepare to get back to school or on the way to or just reach school

\subsection{What did you do on your birthday when you are young?}

\subsection{Do you think it is important for you to celebrate your birthday?}

\section{Social Media}
Note: New Questions for season 9-12
\subsection{Do you like social media?}
I'm a person without too much need for social life
so I only use media to contact with people that I'm been
familiar with, but actually I don't like social media
\subsection{Do you think your friends spend too much time on social media?}
yes, my girlfriend almost spend her all day on a social media application
called Little Red Book
\subsection{Do you want to work in a social media company?}
No, I don't like the work that study on users predilection then
advertising sources that they might have interest on to them
It's both energy consuming and boring, also meaningless

\section{Names}
\subsection{Does your name have a special meaning?}
No, but my former name did have;

heartbroken when I was born cause my mother was in danger
\subsection{How do people choose names for their children?}
pick some characters from poems, quotations or proverbs

to express some good wish or hope the child could have some kind personality
\subsection{Does anyone in your family have the same name with you?}
no one, rarely in China, seems a routine that no repeated names are used in a family
\subsection{Are there any differences between how Chinese name their
children now and in the past?}
aye, in the last century, China is not powerful as it is now, so at that time
we're facing a serious problem of defending for our country, names may contain
that meaning either

now China has been much stronger than 1949, and people would spend more time
%这句话很怪
on literature, so people tend to use phases in poems and books to 
organize children's names

\section{Weather}
\subsection{Do you prefer cold or hot weather?}
I prefer cold weather; more possibility to be snowy and I like snow;

hot weather make me feel depressed
\subsection{Do you prefer dry or wet weather?}
dry weather, giving me a fresh feeling;

while wet weather is like something is mixed up and sticked together;
\subsection{What is the weather like in your hometown?}
cold in winter, hot in summer and usually dry, typically continental climate
\subsection{Do you have the habit of checking the weather forecast?}
no, I always take an umbrella no matter it's sunny or froggy or rainy;
It's not a heavy load and make me prepared for any possible sudden rain;

\section{Singing}
\subsection{Do you like singing?}
No, I'm a bad singer but love listening to music
\subsection{Have you ever learnt to sing?}
Never, not interested and incapable
\subsection{If you sing, who would you sing in front of?}
My friends may be, in a relaxing atmosphere
\subsection{Do you think singing can bring happiness to people?}
I do agree, a way to express oneself always make him or her more comfortable and
bring happiness to thee

\section{Public Transport}
\subsection{What kind of public transport do you usually take?}
bus and subway, I can't distinguish which one is more usual for me;
they are both convenient in China, so it depends what I choose;
\subsection{Did you take public transport when you were a kid?}
the first time I took a bus is when I was 8, from school to my home, alone;
\subsection{Do most people prefer public transport?}
hard to say, all depends;
convenient for somebody, crowded for other guys;
\subsection{When do you usually take public transport?}
most of my time are spent in campus so there isn't a regular timetable for me
to taking public transport, just when it's needed;

\section{Housekeeping and cooking}
\subsection{Do you like cooking?}
Yes, it's inexpensive and I can cook the dish as the flavor I like;
give me a sense of achievement while the dish is finished;
\subsection{Would you like to learn how to cook?}
Yes, seeing delicious food on websites or TV shows makes me eager to cook them myself
\subsection{Who normally does the cooking in your family?}
My dad or me, cause he get off work earlier than my mother;
and if I was home, it should be me to cook for my family;
\subsection{Do you think your home is clean and tidy?}
Yes, cause my parents really care about it;
They basically wipe the floor on every day, and they can't tolerate my room to be
in a mess;
\subsection{Did you do some house cleaning when you were young?}
Yes, house cleaning is not just kind of work, but actually a kind of skill
for everyone to be master at; I think it's quite important, too; 
\subsection{What housework do you like or dislike?}
No particular like or dislike about this, they are just housework to me;
but if possible, I'd choose the easiest one;

\section{Geography}
\subsection{Have you ever studied geography at school?}
Geography is compulsory in Chinese Nine-year compulsory education courses,
and basic geography skill is quite important I assume, like using the map;
I learned it when I was in junior high school and get excellent score;
\subsection{Do you like geography?}
Yes, it's pleasant to know how mountains are formed and where the water is from
in rivers;
Geography also taught me some local conditions and customs of different parts of
the world;
\subsection{Do you want to travel to a country because of its
geographical conditions?}
I did want to travel to some foreign countries for geographical sceneries, like
snow mountains in Switzerland, Cliffs in Scotland and so on;
but actually, there are many kinds of geographical scenario in China mainland,
I can see those domestic scenes either;

\section{Puzzles}
\subsection{Did you like doing puzzles when you were a kid?}
No, math and English is troubling enough for me
\subsection{When do you do puzzles, during trips or when you feel bored?}
this question shouldn't appear
\subsection{Do you like doing word puzzles or number puzzles?}
No, it's difficult for me so I seldom play it;
\subsection{Do you think it is good for old people to do puzzles?}
I think it do have benefits for old people, because keeping brains active 
can help to reduce risks for brain diseases like Alzheimer

\section{Writing}
\subsection{Do you write a lot?}
I wrote a lot in senior high school, cause I had to do so many exams and 
exercises for the entrance to university exam
\subsection{What do you like to write?}
the favorable thing I like to write might be the letter to my girlfriend I guess;
handwriting is a better way to express emotion than typing on the screen;
\subsection{Do you prefer typing or handwriting when you writing something?}
It all depends; for normal and serious documents, I prefer typing on computer;
while for letters to someone or taking notes on class, I prefer handwriting, both
emotional and quickly for me;

\section{Morning routine}
\subsection{Do you like to get up early in the mornings?}
\subsection{What is your morning routine?}
\subsection{Which one is your favorite morning in the whole week?}
\subsection{Do you want to change your daily routines in the future?}

\section{Technology}

\section{Feel Bored}

\section{Meeting Places}

\section{Computers}

\end{document}
